From Big Data to Big Displays\\ High-Performance Visualization at Blue Brain

### 2017-05-10 paper.tex
Tweaks

%% Author and Affiliation (multiple authors with multiple affiliations)
\author{Stefan~Eilemann, et.al.}
\institute{Blue Brain Project, Ecole Polytechnique Federale de Lausanne}

@@

Advances in computer hardware and software have brought raytracing to the point
where it replaces classical rasterization for virtually all use cases in
scientific visualization. On one hand, local illumination for typical OpenGL
data sets (up to hundred million triangles) can be done at similar framerates
to OpenGL~\cite{ospray}. For small datasets, OpenGL performs better, but for
larger data sets raytracing outperforms OpenGL. This is due to a better
scalability with respect to the data set size ($O(\log{N})$ vs $O(n)$).
Furthermore, CPU-based raytracing allows the rendering of larger data sets
without any level-of-detail algorithms due to the larger memory size. Last, but
not least, advanced rendering algorithms such as shadowing, reflections and
global illuminations are significantly easier to implement in a raytracer.

It is for these reasons that interactive raytracing is the future technology for
interactive and offline rendering at Blue Brain. We have developed a first open
source implementation of a visualization engine with different backends:
OSPRay~\cite{ospray} for CPU-based raytracing and OptiX~\cite{optix} for
GPU-based raytracing. These application called Brayns can load and visualize
our data sets in a variety of modes and integrates with our messaging solution
to be accessible from Python.

@@

Livre is an interactive volume rendering engine available under a permissive
open source license. Our main contribution are: an state-of-the-art
implementation of an octree-based level-of-detail selection, a task parallel
rendering pipeline, a multi-GPU based parallel rendering engine, and an easily
extensible renderer through the use of plugin data sources. Furthermore we
propose to create volume representations of different input data using
on-the-fly, interactive transformations of the data, skipping costly
preprocessing steps.

@@

>>>>

%% Author and Affiliation (multiple authors with multiple affiliations)
\author{Stefan~Eilemann, et.al.\thanks{\textit{firstname.lastname}@epfl.ch}}
\institute{Blue Brain Project, Ecole Polytechnique Federale de Lausanne}

@@

Advances in computer hardware and software have brought raytracing to the point
where it replaces classical rasterization for virtually all use cases in
scientific visualization. On one hand, local illumination for typical OpenGL
data sets (up to hundred million triangles) can be done at similar framerates
to OpenGL~\cite{ospray}. For small datasets, OpenGL performs better, but for
larger data sets raytracing outperforms OpenGL. This is due to a better
scalability with respect to the data set size ($O(\log{N})$ vs $O(n)$).
Furthermore, CPU-based raytracing allows the rendering of larger data sets
without any level-of-detail algorithms due to the larger memory size. Last, but
not least, advanced rendering algorithms such as shadowing, reflections and
global illuminations are significantly easier to implement in a raytracer. The
only area where rasterization provides a benefit is for rendering at very high
frame rates, needed for example for immersive visualization.

It is for these reasons that interactive raytracing is the future technology for
interactive and offline rendering at Blue Brain. We have developed a first open
source implementation of a visualization engine with different backends:
OSPRay~\cite{ospray} for CPU-based raytracing and OptiX~\cite{optix} for
GPU-based raytracing. These application called Brayns can load and visualize
our data sets in a variety of modes and integrates with our messaging solution
to be accessible from Python. We are currently integrating the key algorithms
from Livre for out-of-core volume rendering in Brayns.

@@

Livre is an interactive volume rendering engine available under a permissive
open source license. Our main contributions are: an state-of-the-art
implementation of an octree-based level-of-detail selection, a task parallel
rendering pipeline, a multi-GPU based parallel rendering engine, and an easily
extensible renderer through the use of plugin data sources. Furthermore we
propose to create volume representations of different input data using
on-the-fly, interactive transformations of the data, skipping costly
preprocessing steps.

@@

Brayns will become the integrative visualizer
